%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{99}

\bibitem{sertis}
Sertis Corp.,
\textit{Title: "Video Anomaly Detection: An Introduction"},
from: Medium,
In: November 30, 2023,
\url{https://sertiscorp.medium.com/video-anomaly-detection-an-introduction-232bf48c9a8d}

\bibitem{sudhakaran}
Sudhakaran, S., Lanz, O.: Learning to detect violent videos using convolutional long short-term memory. In: 2017 14th IEEE International Conference on Advanced Video and Signal Based Surveillance (AVSS), pp. 1--6. IEEE (2017)

\bibitem{petrocchi}
Petrocchi, S., Giorgi, G., Cimino, M.G.: A real-time deep learning approach for real-world video anomaly detection. In: Proceedings of the 16th International Conference on Availability, Reliability and Security, pp. 1--9 (2021)

\bibitem{vosta2022cnn}
Vosta, S., Yow, K.-C.: A cnn-rnn combined structure for real-world violence detection in surveillance cameras. Applied Sciences \textbf{12}(3), 1021 (2022)

\bibitem{islam2021efficient}
Islam, Z., Rukonuzzaman, M., Ahmed, R., Kabir, M.H., Farazi, M.: Efficient two-stream network for violence detection using separable convolutional lstm. In: 2021 International Joint Conference on Neural Networks (IJCNN), pp. 1--8. IEEE (2021)

\bibitem{zhao2022exploiting}
Zhao, M., Liu, Y., Liu, J., Zeng, X.: Exploiting spatial-temporal correlations for video anomaly detection. In: 2022 26th International Conference on Pattern Recognition (ICPR), pp. 1727--1733. IEEE (2022)

\bibitem{zhang2019temporal}
Zhang, J., Qing, L., Miao, J.: Temporal convolutional network with complementary inner bag loss for weakly supervised anomaly detection. In: 2019 IEEE International Conference on Image Processing (ICIP), pp. 4030--4034. IEEE (2019)

\bibitem{qasim2023video}
Qasim, M., Verdu, E.: Video anomaly detection system using deep convolutional and recurrent models. Results in Engineering \textbf{18}, 101026 (2023)

\bibitem{shao2023video}
Shao, W., Xiao, R., Rajapaksha, P., Wang, M., Crespi, N., Luo, Z., Minerva, R.: Video anomaly detection with NTCN-ML: A novel TCN for multi-instance learning. Pattern Recognition \textbf{143}, 109765 (2023)

\bibitem{Multi-contextual}
Lee, J., Nam, W.-J., Lee, S.-W.: Multi-contextual predictions with vision transformer for video anomaly detection. In: 2022 26th International Conference on Pattern Recognition (ICPR), pp. 1012--1018. IEEE (2022)

\bibitem{attention-anomaly}
Deshpande, K., Punn, N.S., Sonbhadra, S.K., Agarwal, S.: Anomaly detection in surveillance videos using transformer based attention model. In: International Conference on Neural Information Processing, pp. 199--211. Springer (2022)

\bibitem{contrastive}
Chang, S., Li, Y., Shen, S., Feng, J., Zhou, Z.: Contrastive attention for video anomaly detection. IEEE Transactions on Multimedia \textbf{24}, 4067--4076 (2021)

\bibitem{Cross-attention}
Kim, H.H., Yu, S., Yuan, S., Tomasi, C.: Cross-attention transformer for video interpolation. In: Proceedings of the Asian Conference on Computer Vision, pp. 320--337 (2022)

\bibitem{Memory-Token}
Li, Y., Song, X., Xu, T., Feng, Z.: Memory-Token Transformer for Unsupervised Video Anomaly Detection. In: 2022 26th International Conference on Pattern Recognition (ICPR), pp. 3325--3332. IEEE (2022)

\bibitem{multi-view}
Li, Q., Yang, R., Xiao, F., Bhanu, B., Zhang, F.: Attention-based anomaly detection in multi-view surveillance videos. Knowledge-Based Systems \textbf{252}, 109348 (2022)

\bibitem{SwinAnomaly}
Bajgoti, A., Gupta, R., Balaji, P., Dwivedi, R., Siwach, M., Gupta, D.: SwinAnomaly: Real-Time Video Anomaly Detection using Video Swin Transformer and SORT. IEEE Access (2023)

\bibitem{TransCNN}
Ullah, W., Hussain, T., Ullah, F.U.M., Lee, M.Y., Baik, S.W.: TransCNN: Hybrid CNN and transformer mechanism for surveillance anomaly detection. Engineering Applications of Artificial Intelligence \textbf{123}, 106173 (2023)

\bibitem{efficientattention}
Ullah, W., Ullah, A., Hussain, T., Khan, Z.A., Baik, S.W.: An Efficient Anomaly Recognition Framework Using an Attention Residual LSTM in Surveillance Videos. \textit{Sensors} \textbf{21}(8), 2811 (2021). \url{http://dx.doi.org/10.3390/s21082811}

\bibitem{stcnet}
Zhao, M., Liu, Y., Li, J., Zeng, X.: Exploiting Spatial-temporal Correlations for Video Anomaly Detection. arXiv. \url{https://arxiv.org/abs/2211.00829} (2022). \doi{10.48550/ARXIV.2211.00829}

\bibitem{prediction}
Li, T., Comer, M.L., Delp, E.J., Desai, S.R., Mathieson, J.L., Foster, R.H., Chan, M.W.: Anomaly Scoring for Prediction-Based Anomaly Detection in Time Series. In: \textit{2020 IEEE Aerospace Conference}, IEEE (2020). \url{http://dx.doi.org/10.1109/AERO47225.2020.9172442}

\bibitem{end2end}
Lai, Y., Liu, R., Han, Y.: Video Anomaly Detection Via Predictive Autoencoder With Gradient-Based Attention. In: \textit{2020 IEEE International Conference on Multimedia and Expo (ICME)}, IEEE (2020). \url{http://dx.doi.org/10.1109/ICME46284.2020.9102894}

\bibitem{cafe}
Yu, G., Wang, S., Cai, Z., Liu, X., Wu, C.: Effective Video Abnormal Event Detection by Learning A Consistency-Aware High-Level Feature Extractor. In: \textit{Proceedings of the 30th ACM International Conference on Multimedia (MM '22)}, ACM (2022). \url{http://dx.doi.org/10.1145/3503161.3547944}

\bibitem{multivit}
Lee, J.-Y., Nam, W.-J., Lee, S.-W.: Multi-Contextual Predictions with Vision Transformer for Video Anomaly Detection. arXiv. \url{https://arxiv.org/abs/2206.08568} (2022). \doi{10.48550/ARXIV.2206.08568}

\bibitem{Yu2022}
Yu, G., Wang, S., Cai, Z., Liu, X., Wu, C.: Effective Video Abnormal Event Detection by Learning A Consistency-Aware High-Level Feature Extractor. In: \textit{Proceedings of the 30th ACM International Conference on Multimedia (MM '22)}, ACM (2022). \url{http://dx.doi.org/10.1145/3503161.3547944}

\bibitem{pkgnet}
Deng, Z., Chen, D., Deng, S.: Prior Knowledge Guided Network for Video Anomaly Detection. arXiv. \url{https://arxiv.org/abs/2309.01682} (2023). \doi{10.48550/ARXIV.2309.01682}

\bibitem{state}
Wang, Y., Qin, C., Bai, Y., Xu, Y., Ma, X., Fu, Y.: Making Reconstruction-based Method Great Again for Video Anomaly Detection. arXiv. \url{https://arxiv.org/abs/2301.12048} (2023). \doi{10.48550/ARXIV.2301.12048}

\bibitem{ma}
Zhu, Y., Newsam, S.: Motion-Aware Feature for Improved Video Anomaly Detection. arXiv. \url{https://arxiv.org/abs/1907.10211} (2019). \doi{10.48550/ARXIV.1907.10211}

\bibitem{he2015deep}
He, K., Zhang, X., Ren, S., Sun, J.: Deep Residual Learning for Image Recognition. arXiv:1512.03385 (2015).

\bibitem{lei2018simple}
Lei, T., Zhang, Y., Wang, S. I., Dai, H., Artzi, Y.: Simple Recurrent Units for Highly Parallelizable Recurrence. (2018). arXiv:1709.02755 [cs.CL]

\bibitem{lei2021attention}
Lei, T.: When Attention Meets Fast Recurrence: Training Language Models with Reduced Compute. arXiv:2102.12459 [cs.CL] (2021)

\bibitem{zhou2023batchnorm}
Yixuan Zhou, Yi Qu, Xing Xu, Fumin Shen, Jingkuan Song, Hengtao Shen. "BatchNorm-based Weakly Supervised Video Anomaly Detection." arXiv preprint arXiv:2311.15367 (2023).

\bibitem{challenges}
Ren, J., Xia, F., Liu, Y., \& Lee, I. (2021). "Deep video anomaly detection: Opportunities and challenges." In 2021 International Conference on Data Mining Workshops (ICDMW) (pp. 959-966). IEEE.

\bibitem{gan2023contrastive}
Kian Yu Gan, Yu Tong Cheng, Hung-Khoon Tan, Hui-Fuang Ng, Maylor Karhang Leung, Joon Huang Chuah. "Contrastive-regularized U-Net for video anomaly detection." IEEE Access (2023).

\bibitem{dubey20193d}
Shikha Dubey, Abhijeet Boragule, Moongu Jeon. "3D ResNet with ranking loss function for abnormal activity detection in videos." 2019 international conference on control, automation and information sciences (ICCAIS), IEEE (2019).

\bibitem{wu2022self}
Jhih-Ciang Wu, He-Yen Hsieh, Ding-Jie Chen, Chiou-Shann Fuh, Tyng-Luh Liu. "Self-supervised sparse representation for video anomaly detection." European Conference on Computer Vision, Springer (2022).


\end{thebibliography}

\end{document}
